---
title: "October2019_Katie.analysis"
author: "Katie"
date: "10/1/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, message=FALSE, echo=FALSE, error=FALSE, warning=FALSE}
# Calling relevant libraries
rm(list=ls())
library(dplyr)
library(magrittr)
library(ggplot2)
library(grid)
library(gridExtra)
library(ggsignif)
library(tidyr)
library(lme4)
library(lmerTest)
library(yarrr)
library(colorspace)
library(psych)
library(lme4)
#library(Rmisc)
#library(car)
#library(MASS)
#library(Matrix)
#library(mgcv)
#library(plyr)
#library(reshape2)
#library(scales)
#library(stringr)
library(ez)
library(pander)
library(plotrix)
library(sciplot)
library(knitr)
#library(afex)
source("/Users/katieshapiro/Desktop/Adolescent_LiquidFeedback copy/Analyses/Katie/summarySEwithin2.R")
```

#Reading in AD data
```{r}
ADdata.path<- "/Users/katieshapiro/Desktop/Adolescent_LiquidFeedback copy/Katie_Analysis_May2018/AD/Ad_ConsolidatedRewardData.csv"
ADout.path <- "/Users/katieshapiro/Desktop/Adolescent_LiquidFeedback copy/Katie_Analysis_May2018/AD/Analysis/"
ADrunkey.path<-"/Users/katieshapiro/Desktop/Adolescent_LiquidFeedback copy/Katie_Analysis_May2018/AD/Ad_RunKey.csv"
ADfigure.path<-"/Users/katieshapiro/Desktop/Adolescent_LiquidFeedback copy/Katie_Analysis_May2018/AD/Figures/"

#Reading in Redcap data:
RCdata.path <- "/Users/katieshapiro/Desktop/Adolescent_LiquidFeedback copy/Katie_Analysis_May2018/AD/RedCap data/201703146AdolescentM_DATA_LABELS_2018-08-05_1808.csv"
```

#Formatting AD data
```{r}
# Reading the data
ADdata <- read.csv("/Users/katieshapiro/Desktop/Adolescent_LiquidFeedback copy/Katie_Analysis_May2018/AD/Ad_ConsolidatedRewardData.csv",header=TRUE)

ADdata<-read.csv(ADdata.path, header=TRUE) %>% select(-X)

ADrunkey<-read.csv(ADrunkey.path,header=TRUE)
ADrunkey<-subset(ADrunkey, !ADrunkey$exclude.=="Yes")

#formatting incentive data
ADdata<-select(ADrunkey, subID, block, liqType, older18, age) %>%
  inner_join(ADdata, by=c("subID","block")) %>%
  mutate(subRewarded = (RT<critRT & ACC==1)*1, subError = (ACC==0 & RT>critRT)*1,
         moneynumber = factor(reward, levels = c("Reward1","Reward2","Reward4"), labels = c(1,2,4)),
         money = factor(reward, levels = c("Reward1","Reward2","Reward4"), labels = c("$","$$","$$$$")),
         rewCode = factor(reward, levels=c("Reward1","Reward2","Reward4"), labels=c(-1,0,1)),
         liqCode = factor(liqType, levels=c("Juice","Neutral","Saltwater"), labels=c(1,0,-1)),
         blockCode = factor(block, levels=c(6,7,8), labels=c(-1,0,1)),
         block = factor(block, levels=c(6,7,8), labels=c(1:3)))
ADdata$rewCode <- as.numeric(levels(ADdata$rewCode)[ADdata$rewCode])
ADdata$liqCode <- as.numeric(levels(ADdata$liqCode)[ADdata$liqCode])
ADdata$blockCode <- as.numeric(levels(ADdata$blockCode)[ADdata$blockCode])

# summarized mean for each subject, grouped by condition
# note that filter(!is.na(subRewarded)) means excluding the people who didnt answer
ADdata.means = group_by(ADdata, subID, block, liqType, money, age) %>% filter(!is.na(subRewarded)) %>%
  dplyr::summarise(n=n(), meanRR = mean(subRewarded), meanACC = mean(ACC), meanErr = mean(subError))
ADdataRT.means = group_by(ADdata, subID, age, block, liqType, money) %>% filter(!is.na(subRewarded), ACC==1) %>% 
  dplyr::summarise(n=n(), meanRT = mean(RT))

ADdata.means.money = group_by(ADdata, subID, money, age) %>% filter(!is.na(subRewarded)) %>%
  dplyr::summarise(n=n(), meanRR = mean(subRewarded), meanACC = mean(ACC), meanErr = mean(subError), meanRT=mean(RT))
ADdata.means.money$group <- "AD"

ADdata.means.liquid = group_by(ADdata, subID, liqType, age, RT) %>% filter(!is.na(subRewarded)) %>%
  dplyr::summarise(n=n(), meanRR = mean(subRewarded), meanACC = mean(ACC), meanErr = mean(subError), meanRT = mean(RT))
ADdata.means.liquid$group <- "AD"

# Create data frame where each row pertains to an individual subject
# note that filter(!is.na(subRewarded)) means taking out the people who didnt answer
ADsubjectMeans = group_by(ADdata, subID, age) %>% filter(!is.na(subRewarded)) %>%
  dplyr::summarise(n=n(), meanRR = mean(subRewarded), meanACC = mean(ACC), meanErr = mean(subError))
ADsubjectMeansRT = group_by(ADdata, subID) %>% filter(!is.na(subRewarded), ACC==1) %>%
  dplyr::summarise(n=n(), meanRT = mean(RT))

ADsubjectMeans <-data.frame(ADsubjectMeans, ADsubjectMeansRT$meanRT)
names(ADsubjectMeans)[names(ADsubjectMeans) == "subjectMeansRT.meanRT"] <- "meanRT"
```

#Additional AD formatting
```{r}
ADsaltwaterData <- subset(ADdata, liqType == "Saltwater")
ADsaltwaterMeans <- group_by(ADsaltwaterData, subID, age) %>% filter(!is.na(subRewarded)) %>%
    dplyr::summarise(n=n(), meanRR = mean(subRewarded), meanACC = mean(ACC), meanErr = mean(subError))

ADjuiceData <- subset(ADdata, liqType == "Juice")
ADjuiceMeans <- group_by(ADjuiceData, subID, age) %>% filter(!is.na(subRewarded)) %>%
    dplyr::summarise(n=n(), meanRR = mean(subRewarded), meanACC = mean(ACC), meanErr = mean(subError))
  
ADneutralData <- subset(ADdata, liqType == "Neutral")
ADneutralMeans <- group_by(ADneutralData, subID, age) %>% filter(!is.na(subRewarded)) %>%
    dplyr::summarise(n=n(), meanRR = mean(subRewarded), meanACC = mean(ACC), meanErr = mean(subError))

# Data JUST FOR JUICE, just for $ vs. $$$$
ADjuiceCondition <- ADdata.means[!(ADdata.means$liqType== "Saltwater") & !(ADdata.means$liqType== "Neutral") & !(ADdata.means$money== "$$"),]
ADjuiceCondition$group <- "AD"

# Data JUST FOR SALTWATER, just for $ vs. $$$$
ADsaltwaterCondition <- ADdata.means[!(ADdata.means$liqType== "Juice") & !(ADdata.means$liqType== "Neutral") & !(ADdata.means$money== "$$"),]
ADsaltwaterCondition$group <- "AD"

# Data for JUST $, juice vs. saltwater
ADoneDScondition <- ADdata.means[!(ADdata.means$money== "$$") & !(ADdata.means$money== "$$$$") & !(ADdata.means$liqType== "Neutral"),] 
ADoneDScondition$group <- "AD"

# Data for JUST $$, juice vs. saltwater
ADtwoDScondition <- ADdata.means[!(ADdata.means$money== "$") & !(ADdata.means$money== "$$$$") & !(ADdata.means$liqType== "Neutral"),]
ADtwoDScondition$group <- "AD"

# Data for JUST $$$$, juice vs. saltwater
ADfourDScondition <- ADdata.means[!(ADdata.means$money== "$") & !(ADdata.means$money== "$$") & !(ADdata.means$liqType== "Neutral"),]
ADfourDScondition$group <- "AD"

# summarise incentive data using dummy coded variables 
ADdata.means0 = group_by(ADdata, age, subID, liqCode, rewCode) %>%
  filter(!is.na(subRewarded)) %>% 
  dplyr::summarise(n = n(), meanRR = mean(subRewarded), meanACC = mean(ACC), meanErr = mean(subError)) 
ADdataRT.means0 = group_by(ADdata, subID, liqCode, rewCode) %>%
  filter(!is.na(subRewarded), ACC==1) %>% 
  dplyr::summarise(n = n(), meanRT = mean(RT)) 

# task switching data, switch costs
ADdata.means.switch = group_by(ADdata, subID, block, liqType, money,taskSwitch) %>% 
  filter(!is.na(subRewarded), trial!=1) %>%
  dplyr::summarise(n=n(), meanRR = mean(subRewarded), meanACC = mean(ACC), meanErr = mean(subError))
ADdataRT.means.switch = group_by(ADdata, subID, block, liqType, money,taskSwitch) %>% 
  filter(!is.na(subRewarded), ACC==1, trial!=1) %>% 
  dplyr::summarise(n=n(), meanRT = mean(RT))
```


#Reading in YA data
```{r}
YAdata.path <- "/Users/katieshapiro/Desktop/Adolescent_LiquidFeedback copy/YoungAdult_ConsolidatedRewardData.csv"
YAout.path <- "/Users/katieshapiro/Desktop/Adolescent_LiquidFeedback copy/"
YArunkey.path<-"/Users/katieshapiro/Desktop/Adolescent_LiquidFeedback copy/Katie_Analysis_May2018/AD/Ya_RunKey.csv"
```


#Formatting YA data
```{r}
# Reading the data
YAdata<- read.csv("/Users/katieshapiro/Desktop/Adolescent_LiquidFeedback copy/YoungAdult_ConsolidatedRewardData.csv", header=TRUE)

YArunkey<-read.csv(YArunkey.path,header=TRUE)

#formatting incentive data
YAdata<-select(YArunkey, subID, block, liqType, age) %>%
  inner_join(YAdata, by=c("subID","block")) %>%
  mutate(subRewarded = (RT<critRT & ACC==1)*1, subError = (ACC==0 & RT>critRT)*1,
         #moneynumber = factor(reward, levels = c("Reward1","Reward2","Reward4"), labels = c(1,2,4)),
         reward <- YAdata$reward,
         moneynumber = factor(reward, levels = c("Reward1","Reward2","Reward4"), labels = c(1,2,4)),
         money = factor(reward, levels = c("Reward1","Reward2","Reward4"), labels = c("$","$$","$$$$")),
         rewCode = factor(reward, levels=c("Reward1","Reward2","Reward4"), labels=c(-1,0,1)),
         liqCode = factor(liqType, levels=c("juice","neutral","saltwater"), labels=c(1,0,-1)),
         blockCode = factor(block, levels=c(6,7,8), labels=c(-1,0,1)),
         block = factor(block, levels=c(7:9), labels=c(1:3)))
YAdata$rewCode <- as.numeric(levels(YAdata$rewCode)[YAdata$rewCode])
YAdata$liqCode <- as.numeric(levels(YAdata$liqCode)[YAdata$liqCode])

# summarized mean for each subject, grouped by condition
YAdata.means = group_by(YAdata, subID, block, liqType, money, age) %>% filter(!is.na(subRewarded)) %>%
  dplyr::summarise(n=n(), meanRR = mean(subRewarded), meanACC = mean(ACC), meanErr = mean(subError))
YAdataRT.means = group_by(YAdata, subID, block, liqType, money) %>% filter(!is.na(subRewarded), ACC==1) %>% 
  dplyr::summarise(n=n(), meanRT = mean(RT))

########
YAsubjectMeans = group_by(YAdata, subID, age) %>% filter(!is.na(subRewarded)) %>%
  dplyr::summarise(n=n(), meanRR = mean(subRewarded), meanACC = mean(ACC), meanErr = mean(subError))
YAsubjectMeansRT = group_by(YAdata, subID) %>% filter(!is.na(subRewarded), ACC==1) %>%
  dplyr::summarise(n=n(), meanRT = mean(RT))

YAsubjectMeans <-data.frame(YAsubjectMeans, YAsubjectMeansRT$meanRT)
names(YAsubjectMeans)[names(YAsubjectMeans) == "YAsubjectMeansRT.meanRT"] <- "meanRT"

YAdata.means.money = group_by(YAdata, subID, money, age) %>% filter(!is.na(subRewarded)) %>%
  dplyr::summarise(n=n(), meanRR = mean(subRewarded), meanACC = mean(ACC), meanErr = mean(subError))

YAdata.means.liquid = group_by(YAdata, subID, liqType, age) %>% filter(!is.na(subRewarded)) %>%
  dplyr::summarise(n=n(), meanRR = mean(subRewarded), meanACC = mean(ACC), meanErr = mean(subError))
```


# Additional YA formatting
```{r}
# Data JUST FOR JUICE, just for $ vs. $$$$
YAjuiceCondition <- YAdata.means[!(YAdata.means$liqType== "Saltwater") & !(YAdata.means$liqType== "Neutral") & !(YAdata.means$money== "$$"),]
YAjuiceCondition$group <- "YA"

# Data JUST FOR SALTWATER, just for $ vs. $$$$
YAsaltwaterCondition <- YAdata.means[!(YAdata.means$liqType== "Juice") & !(YAdata.means$liqType== "Neutral") & !(YAdata.means$money== "$$"),]
YAsaltwaterCondition$group <- "YA"

# Data for JUST $, juice vs. saltwater
YAoneDScondition <- YAdata.means[!(YAdata.means$money== "$$") & !(YAdata.means$money== "$$$$") & !(YAdata.means$liqType== "Neutral"),] 
YAoneDScondition$group <- "YA"

# Data for JUST $$, juice vs. saltwater
YAtwoDScondition <- YAdata.means[!(YAdata.means$money== "$") & !(YAdata.means$money== "$$$$") & !(YAdata.means$liqType== "Neutral"),]
YAtwoDScondition$group <- "YA"

# Data for JUST $$$$, juice vs. saltwater
YAfourDScondition <- YAdata.means[!(YAdata.means$money== "$") & !(YAdata.means$money== "$$") & !(YAdata.means$liqType== "Neutral"),]
YAfourDScondition$group <- "YA"

# summarise incentive data using dummy coded variables 
YAdata.means0 = group_by(YAdata, subID, liqCode, rewCode) %>%
  filter(!is.na(subRewarded)) %>% 
  dplyr::summarise(n = n(), meanRR = mean(subRewarded), meanACC = mean(ACC), meanErr = mean(subError)) 
YAdataRT.means0 = group_by(YAdata, subID, liqCode, rewCode) %>%
  filter(!is.na(subRewarded), ACC==1) %>% 
  dplyr::summarise(n = n(), meanRT = mean(RT)) 

# task switching data, switch costs
YAdata.means.switch = group_by(YAdata, subID, block, liqType, money,taskSwitch) %>% 
  filter(!is.na(subRewarded), trial!=1) %>%
  dplyr::summarise(n=n(), meanRR = mean(subRewarded), meanACC = mean(ACC), meanErr = mean(subError))
YAdataRT.means.switch = group_by(YAdata, subID, block, liqType, money,taskSwitch) %>% 
  filter(!is.na(subRewarded), ACC==1, trial!=1) %>% 
  dplyr::summarise(n=n(), meanRT = mean(RT))
```

#Read in / Format AD baseline data
```{r}
BLdata.path<- "/Users/katieshapiro/Desktop/Adolescent_LiquidFeedback copy/Katie_Analysis_May2018/AD/Ad_ConsolidatedBaselineData.csv"
BLout.path <- "/Users/katieshapiro/Desktop/Adolescent_LiquidFeedback copy/Katie_Analysis_May2018/AD/"

BLdata <- read.csv("/Users/katieshapiro/Desktop/Adolescent_LiquidFeedback copy/Katie_Analysis_May2018/AD/Ad_ConsolidatedBaselineData.csv", header=TRUE)

BLdata.means = group_by(BLdata, baseline2.Subject, baseline2.Block) %>%
  dplyr::summarise(n=n(), meanACC = mean(baseline2.Target.ACC), meanRT = mean(baseline2.Target.RT))

runkeySummary = group_by(ADrunkey, subID, age,) %>%
  dplyr::summarise(n=n(), critRT = mean(critRT))

#tack on the runkeySummary, which has age, onto BLdata.means
newBLdata <- cbind(BLdata.means, runkeySummary)
newBLdata$n <- NULL
newBLdata$subID1 <- NULL
newBLdata$n1 <- NULL

colnames(newBLdata)[colnames(newBLdata)=="baseline2.Subject"] <- "subID"
colnames(newBLdata)[colnames(newBLdata)=="baseline2.Block"] <- "block"

data.base<-read.csv(BLdata.path, header = TRUE)
colnames(data.base)[colnames(data.base)=="baseline2.Subject"] <- "subID"
colnames(data.base)[colnames(data.base)=="baseline2.CriterionResult"] <- "crit"
colnames(data.base)[colnames(data.base)=="baseline2.Block"] <- "block"
colnames(data.base)[colnames(data.base)=="baseline2.Trial"] <- "trial"
colnames(data.base)[colnames(data.base)=="baseline2.Subject"] <- "subID"
colnames(data.base)[colnames(data.base)=="baseline2.Congruency"] <- "congruency"
colnames(data.base)[colnames(data.base)=="baseline2.Target.ACC"] <- "ACC"
colnames(data.base)[colnames(data.base)=="baseline2.Target.RESP"] <- "RESP"
colnames(data.base)[colnames(data.base)=="baseline2.Target.RT"] <- "RT"
colnames(data.base)[colnames(data.base)=="baseline2.TaskSwitch"] <- "task switch"

# Merge baseline and incentive data
cond.RT.base <- data.base %>% filter(ACC==1) %>% select(subID, RT)
cond.RT.base = group_by(cond.RT.base, subID) %>%
  dplyr::summarise(n=n(), meanRT = mean(RT))
cond.RT.base$condition = "baseline"
cond.RT.base$n = NULL 
cond.RT.base$age = runkeySummary$age
cond.RT.base$group = c("ages 13-15", "ages 16-18", "ages 16-18", "ages 13-15", "ages 13-15", "ages 13-15", "ages 13-15", "ages 16-18", "ages 16-18", "ages 13-15", "ages 13-15", "ages 16-18", "ages 16-18", "ages 13-15", "ages 16-18", "ages 13-15", "ages 16-18", "ages 16-18", "ages 16-18", "ages 13-15", "ages 13-15", "ages 13-15", "ages 16-18", "ages 16-18", "ages 16-18", "ages 16-18", "ages 16-18", "ages 16-18", "ages 16-18", "ages 13-15", "ages 13-15", "ages 13-15", "ages 13-15", "ages 13-15", "ages 13-15", "ages 16-18", "ages 13-15", "ages 16-18", "ages 16-18", "ages 16-18", "ages 13-15", "ages 13-15", "ages 16-18", "ages 16-18", "ages 13-15", "ages 13-15", "ages 16-18", "ages 13-15", "ages 13-15", "ages 13-15", "ages 16-18")

#dataRT.means already subsetted so ACC==1
cond.RT.rew <- ADdataRT.means %>% select(subID, meanRT)
cond.RT.rew = group_by(cond.RT.rew, subID) %>% 
  dplyr::summarise(n=n(), meanRT = mean(meanRT))
cond.RT.rew$condition = "reward"
cond.RT.rew$n = NULL 
cond.RT.rew$age = runkeySummary$age
cond.RT.rew$group = c("ages 13-15", "ages 16-18", "ages 16-18", "ages 13-15", "ages 13-15", "ages 13-15", "ages 13-15", "ages 16-18", "ages 16-18", "ages 13-15", "ages 13-15", "ages 16-18", "ages 16-18", "ages 13-15", "ages 16-18", "ages 13-15", "ages 16-18", "ages 16-18", "ages 16-18", "ages 13-15", "ages 13-15", "ages 13-15", "ages 16-18", "ages 16-18", "ages 16-18", "ages 16-18", "ages 16-18", "ages 16-18", "ages 16-18", "ages 13-15", "ages 13-15", "ages 13-15", "ages 13-15", "ages 13-15", "ages 13-15", "ages 16-18", "ages 13-15", "ages 16-18", "ages 16-18", "ages 16-18", "ages 13-15", "ages 13-15", "ages 16-18", "ages 16-18", "ages 13-15", "ages 13-15", "ages 16-18", "ages 13-15", "ages 13-15", "ages 13-15", "ages 16-18")

cond.RT<-rbind(cond.RT.base,cond.RT.rew) 



# Merge baseline and incentive data
cond.ACC.base <- data.base  %>% select(subID, ACC)
cond.ACC.base = group_by(cond.ACC.base, subID) %>%
  dplyr::summarise(n=n(), meanACC = mean(ACC))
cond.ACC.base$condition = "baseline"
cond.ACC.base$n = NULL 

cond.ACC.rew <- ADdata.means %>% select(subID, meanACC)
cond.ACC.rew = group_by(cond.ACC.rew, subID) %>% 
  dplyr::summarise(n=n(), meanACC = mean(meanACC))
cond.ACC.rew$condition = "reward"
cond.ACC.rew$n = NULL 

cond.ACC<-rbind(cond.ACC.base,cond.ACC.rew)
```

#Read in AD redcap data
```{r}
RCdata.path <- "/Users/katieshapiro/Desktop/Adolescent_LiquidFeedback copy/Katie_Analysis_May2018/AD/RedCap data/201703146AdolescentM_DATA_LABELS_2018-08-05_1808.csv"

RCout.path <- "/Users/katieshapiro/Desktop/Adolescent_LiquidFeedback copy/Katie_Analysis_May2018/AD/RedCap data/"
```


#Format AD redcap data
```{r}
RCdata <- read.csv("/Users/katieshapiro/Desktop/Adolescent_LiquidFeedback copy/Katie_Analysis_May2018/AD/RedCap data/201703146AdolescentM_DATA_LABELS_2018-08-05_1808.csv", header=TRUE)

#1 - like/dislike JUICE
#2 - intensity JUICE
#3 - like/dislike SALTWATER
#4 - intensity SALTWATER
#5 - like/dislike NEUTRAL
#6 - intensity NEUTRAL

#X - BAS Drive
#X.1 - BAS FUN
#X.2 - BAS Reward
#X.3 - BIS

#SubjData <- select(RCdata, Study.ID, BAS.Drive, BAS.Fun, BAS.Reward, BIS)
SubjData <- select(RCdata, Study.ID, X, X.1, X.2, X.3, X1.7.liking.JUICE, X1.7.intensity.JUICE, X1.7.liking.SALTWATER, X1.7.intensity.SALTWATER, X1.7.liking.NEUTRAL, X1.7.intensity.NEUTRAL, Mot.1DS.JUICE, Like.1DS.JUICE, Mot.1DS.SALTWATER, Like.1DS.SALTWATER, Mot.1DS.NEUTRAL, Like.1DS.NEUTRAL, Mot.2DS.JUICE, Like.2DS.JUICE, Mot.2DS.SALTWATER, Like.2DS.SALTWATER, Mot.2DS.NEUTRAL, Like.2DS.NEUTRAL, Mot.4DS.JUICE, Like.4DS.JUICE, Mot.4DS.SALTWATER, Like.4DS.SALTWATER, Mot.4DS.NEUTRAL, Like.4DS.NEUTRAL)

SubjData <- SubjData[-40,]

colnames(SubjData)[colnames(SubjData)=="X"] <- "BASDrive"
colnames(SubjData)[colnames(SubjData)=="X.1"] <- "BASFUN"
colnames(SubjData)[colnames(SubjData)=="X.2"] <- "BASReward"
colnames(SubjData)[colnames(SubjData)=="X.3"] <- "BIS"
colnames(SubjData)[colnames(SubjData)=="X1.7.liking.JUICE"] <- "Juice Likert"
colnames(SubjData)[colnames(SubjData)=="X1.7.intensity.JUICE"] <- "Juice Intensity"
colnames(SubjData)[colnames(SubjData)=="X1.7.liking.SALTWATER"] <- "Saltwater Likert"
colnames(SubjData)[colnames(SubjData)=="X1.7.intensity.SALTWATER"] <- "Saltwater Intensity"
colnames(SubjData)[colnames(SubjData)=="X1.7.liking.NEUTRAL"] <- "Neutral Likert"
colnames(SubjData)[colnames(SubjData)=="X1.7.intensity.NEUTRAL"] <- "Neutral Intensity"
```



# PLOT I. (TB): BASELINE VS. INCENTIVE EFFECTS 

#All adolescents - with data points plotted
```{r}
RT.sum=summarySEwithin2(data=cond.RT, measurevar = "meanRT", withinvars = c("condition"),
                        idvar = "subID")
p1a<-ggplot(data = RT.sum, mapping =aes(x=condition, y = meanRT)) +
  geom_bar(stat = "identity", color="black") +
  geom_errorbar(aes(ymin=meanRT-ci, ymax=meanRT+ci), width=0.2) +
  geom_point(data = cond.RT, color="red",
             position = position_jitter(h=0, w=0.2), alpha=0.75) +
  xlab("Condition") + ylab("Response Time (ms)") +
  labs(fill = "Block") +
  ggtitle("Use theme(plot.title=element_text(hjust=0.5) to center") + theme(plot.title=element_text(hjust=0.5)) +
   ggtitle("Adolescents' Response Time in Baseline vs. Incentive Trials") +
  coord_cartesian(ylim=c(0,1500)) +
  scale_fill_brewer(palette="Set1") +
  theme(#plot.title=element_text(size=22,face="bold", vjust=2),
    axis.title=element_text(size=12,face = "bold"),
    axis.text=element_text(size=14),
    legend.position=c(.85,.85),
    legend.box.background = element_rect(colour = "black"),
    strip.text.x = element_text(size = 12))
p1a
```

#All adolescents - without data points plotted
```{r}
RT.sum=summarySEwithin2(data=cond.RT, measurevar = "meanRT", withinvars = c("condition"),
                        idvar = "subID")
p1a<-ggplot(data = RT.sum, aes(x=condition, y = meanRT)) +
  geom_bar(position=position_dodge(width=0.8), color="black",
           stat="identity", width=0.8, fill = "red") +
  geom_errorbar(position=position_dodge(width=0.8),
                aes(ymin=meanRT-se, ymax=meanRT+se), width=.2) +
  xlab("Condition") + ylab("Response Time (ms)") +
  labs(fill = "Block") +
  ggtitle("Use theme(plot.title=element_text(hjust=0.5) to center") + theme(plot.title=element_text(hjust=0.5)) +
   ggtitle("Adolescents' Response Time in Baseline vs. Incentive Trials") +
  coord_cartesian(ylim=c(400,1000)) +
  scale_fill_brewer(palette="Set1") +
  theme(#plot.title=element_text(size=22,face="bold", vjust=2),
    axis.title=element_text(size=12,face = "bold"),
    axis.text=element_text(size=14),
    legend.position=c(.85,.85),
    legend.box.background = element_rect(colour = "black"),
    strip.text.x = element_text(size = 12))
p1a
```

```{r}
ezANOVA(data=cond.RT, dv=meanRT, wid=subID, within=condition)
```

```{r}
kable(RT.sum, caption = "RT by condition")
```


# Adolescents 13-15 vs. 16-18 years old (baseline vs. incentive)
```{r}
RT.sum=summarySEwithin2(data=cond.RT, measurevar = "meanRT", withinvars = c("group", "condition"), idvar = "subID")
p1b<-ggplot(data = RT.sum, aes(x=condition, y=meanRT, fill="group")) +
  geom_bar(position=position_dodge(width=0.8), color="black",
           stat="identity", width=0.8, fill = "red") +
  geom_errorbar(position=position_dodge(width=0.8),
                aes(ymin=meanRT-se, ymax=meanRT+se), width=.2) +
  xlab("Condition") + ylab("Response Time (ms)") +
  labs(fill = "Block") +
  ggtitle("Use theme(plot.title=element_text(hjust=0.5) to center") + theme(plot.title=element_text(hjust=0.5)) +
   ggtitle("Adolescents' Response Time in Baseline vs. Incentive Trials") +
  coord_cartesian(ylim=c(400,1000)) +
  scale_fill_brewer(palette="Set1") +
  theme(#plot.title=element_text(size=22,face="bold", vjust=2),
    axis.title=element_text(size=12,face = "bold"),
    axis.text=element_text(size=14),
    legend.position=c(.85,.85),
    legend.box.background = element_rect(colour = "black"),
    strip.text.x = element_text(size = 12))
p1b
```

#fix graph ^
#add stats
#get young adult baseline data for comparison


# PLOT II. (TB): REWARD RATE

#Adolescent reward rate (each age)
```{r}
RR.agebin=summarySEwithin2(data = ADdata.means, measurevar = "meanRR", withinvars = "age", idvar = "subID")
p2a<-ggplot(RR.agebin, aes(x=age, y=meanRR)) + 
  geom_bar(position=position_dodge(width=0.8),  stat="identity", width=0.8, fill="green") +
  geom_errorbar(position=position_dodge(width=0.8), aes(ymin=meanRR-se, ymax=meanRR+se), width=.2) +  
  labs(x="Age Bin",y="Reward Rate") +
  ggtitle("Use theme(plot.title=element_text(hjust=0.5) to center") + theme(plot.title=element_text(hjust=0.5)) +
  ggtitle("Adolescent Task Performance by Age Bin") + 
  #scale_x_discrete(labels=c("win","avoid losing")) +
  coord_cartesian(ylim=c(.2,.8)) +
  theme(#panel.background = element_blank(), panel.grid.major= element_blank(),
        panel.grid.minor=element_blank(),
        plot.title=element_text(size=22,face="bold", vjust=2),
        axis.title=element_text(size=12,face = "bold"),
        axis.text=element_text(size=14),
        legend.position="none")

p2a
```

#Adolescent reward rate, 13-15 and 16-18 and young adults
```{r}
threeRR.agebin=summarySEwithin2(data = combinedRR.agebin, measurevar = "meanRR", withinvars = "age.group", idvar = "age")

threeRR.agebin <- threeRR.agebin[c(3,1,2),]

p2b<-ggplot(threeRR.agebin, aes(x=age.group, y=meanRR)) + 
  geom_bar(position=position_dodge(width=0.8),  stat="identity", width=0.8, fill="green") +
  geom_errorbar(position=position_dodge(width=0.8), aes(ymin=meanRR-se, ymax=meanRR+se), width=.2) +  
  labs(x="Age Bin",y="Reward Rate") +
  ggtitle("Use theme(plot.title=element_text(hjust=0.5) to center") + theme(plot.title=element_text(hjust=0.5)) +
  ggtitle("Adolescent - Young Adult Task Performance by Age Bin") + 
  #scale_x_discrete(labels=c("win","avoid losing")) +
  coord_cartesian(ylim=c(.2,.8)) +
  theme(#panel.background = element_blank(), panel.grid.major= element_blank(),
        panel.grid.minor=element_blank(),
        plot.title=element_text(size=14,face="bold", vjust=2),
        axis.title=element_text(size=12,face = "bold"),
        axis.text=element_text(size=14),
        legend.position="none")

p2b
```

#adolescent to young adult continuum 
```{r}
ADsubjectMeans <- data.frame(ADsubjectMeans, age.group = "adolescent")
YAsubjectMeans <- data.frame(YAsubjectMeans, age.group = "young adult")

combined <- rbind(ADsubjectMeans, YAsubjectMeans)

yaRR.agebin <- summarySEwithin2(data = YAdata.means, measurevar = "meanRR", withinvars = "age", idvar = "subID")
yaRR.agebin$age.group <- "young adult"

adRR.agebin=summarySEwithin2(data = ADdata.means, measurevar = "meanRR", withinvars = "age", idvar = "subID")
adRR.agebin$age.group <- "adolescent"

combinedRR.agebin <- rbind(adRR.agebin, yaRR.agebin)
#change "age" in combinedRR.agebin from factor to integer
combinedRR.agebin$age <- as.numeric(levels(combinedRR.agebin$age))[combinedRR.agebin$age]


figure2c <- ggplot(data = combinedRR.agebin, aes(x = age, y=meanRR)) +
  geom_bar(data=combinedRR.agebin, stat="identity", position = position_dodge(width = 0.8), width = 0.8, color = "black") +
  geom_errorbar(position=position_dodge(width=0.8), aes(ymin=meanRR-se, ymax=meanRR+se), width=.2) +  
  geom_point(data=combined, mapping = aes(x=age, y=meanRR, between=age.group), 
             stat="identity", position=position_jitter(w=.3), alpha=0.5) +
  geom_hline(yintercept = .30, linetype="dashed") +
  geom_hline(yintercept = .35) +
  geom_hline(yintercept = .25) +
  #annotate("rect", xmin = 0, xmax = 3, ymin = .25, ymax = .35,
        #alpha = .2) + 
  labs(x="Age Bin",y="Reward Rate") +
  facet_grid(.~age.group, scales = "free_x") +
  #ggtitle("Task Performance Across Money") + 
  #scale_x_discrete(labels=c("younger","older")) +
  #scale_x_continuous(breaks=c(12:19), labels=c(13:18),limits=c(13,18)) + 
  coord_cartesian(ylim=c(0,.8)) +
  theme(panel.grid.minor=element_line(),
        plot.title=element_text(size=22,face="bold", vjust=2),
        axis.title=element_text(size=14,face = "bold"),
        axis.text=element_text(size=12))
        #legend.position="none")

figure2c
```


#add stats for the last 3 graphs



# PLOT III. (TB): INCENTIVE INTEGRATION

#Adolescent incentive integration
```{r}
RR.sum=summarySEwithin2(data = ADdata.means, measurevar = "meanRR", withinvars = c("money","liqType"), idvar="subID")
p3a<-ggplot(RR.sum, aes(x=liqType, y=meanRR, fill=money)) + 
  geom_bar(position=position_dodge(width=0.8), color="black", stat="identity", width=0.8) +
  geom_errorbar(position=position_dodge(width=0.8), aes(ymin=meanRR-se, ymax=meanRR+se), width=.2) +  
  #facet_grid(.~money) +
  labs(x="Incentive",y="Reward Rate") +
  #scale_x_discrete(labels=c("win","avoid losing")) +
  ggtitle("Use theme(plot.title=element_text(hjust=0.5) to center") + theme(plot.title=element_text(hjust=0.5)) +
  ggtitle("Adolescent Reward Rate Across Incentive Conditions") + 
  coord_cartesian(ylim=c(.3,.85)) +
  theme(#panel.background = element_blank(), panel.grid.major= element_blank(),
        panel.grid.minor=element_blank(),
        plot.title=element_text(size=18,face="bold", vjust=2),
        axis.title=element_text(size=12,face = "bold"),
        axis.text=element_text(size=14),
        strip.text.x = element_text(size=12, face = "bold"))
        #legend.position="none")

p3a
```


```{r}
ezANOVA(data=ADdata.means, dv=meanRR, wid=subID, within=c(liqType, money))
```

## Generalized Linear Mixed Effects Models: Reward Rate Effects by Monetary Incentive and Liquid Incentive
```{r}
#m.RR.moneyxliq<-glmer(formula = subRewarded ~ moneynumber * liqCode + (1+moneynumber|subID),
#          data = ADdata, family = binomial)
#summary(m.RR.moneyxliq)
```

#Adolescent money performance -by age
```{r}
p3b <- ggplot(RR.moneyAgebin, aes(x=age, y=meanRR, fill=money))+
  geom_bar(position=position_dodge(width=0.8), color="black", stat="identity", width=0.8) +
  #geom_smooth(method='lm') +
  geom_errorbar(position=position_dodge(width=0.8), aes(ymin=meanRR-se, ymax=meanRR+se), width=.2) +
  labs(x="Age bin",y="Reward Rate") +
  ggtitle("Use theme(plot.title=element_text(hjust=0.5) to center") + theme(plot.title=element_text(hjust=0.5)) +
  ggtitle("Reward Rate per Monetary Condition
  between Age Bins")
  #scale_x_discrete(labels=c("win","avoid losing")) +
  coord_cartesian(ylim= c(0.4,0.8)) +
  #coord_cartesian(xlim= c(13,18)) +
  theme(panel.background = element_blank(), panel.grid.major= element_blank(),
        panel.grid.minor=element_blank(),
        plot.title=element_text(size=22,face="bold", vjust=2),
        axis.title=element_text(size=12,face = "bold"),
        axis.text=element_text(size=14))
       # scale_color_manual(values = c("AD" = "black", "YA" = "red")))
        #legend.position="none")
p3b
```

```{r}
ezANOVA(data=ADdata.means.money, dv=meanRR, wid=subID, within=c(money), between=age)
```

## Generalized Linear Mixed Effects Models: Reward Rate Effects by Monetary Incentive and Age
```{r}
# m.RR.moneyxage<-glmer(formula = subRewarded ~ moneynumber * age + (1+moneynumber|subID),
#           data = ADdata, family = binomial)
# summary(m.RR.moneyxage)
```


#Adolescent liquid performance -by age
```{r}
RR.liquidAgebin=summarySEwithin2(data=ADdata.means.liquid, measurevar = "meanRR", withinvars = c("age", "liqType"), idvar="subID")
p3c <- ggplot(RR.liquidAgebin, aes(x=age, y=meanRR, fill=liqType))+
  geom_bar(position=position_dodge(width=0.8), color="black", stat="identity", width=0.8) +
  #geom_smooth(method='lm') +
  geom_errorbar(position=position_dodge(width=0.8), aes(ymin=meanRR-se, ymax=meanRR+se), width=.2) +
  labs(x="Age bin",y="Reward Rate") +
  ggtitle("Use theme(plot.title=element_text(hjust=0.5) to center") + theme(plot.title=element_text(hjust=0.5)) +
  ggtitle("Reward Rate per Liquid Condition 
  between Age Bins") + 
  #scale_x_discrete(labels=c("win","avoid losing")) +
  coord_cartesian(ylim= c(0.4,0.8)) +
  #coord_cartesian(xlim= c(13,18)) +
  theme(#panel.background = element_blank(), panel.grid.major= element_blank(),
        panel.grid.minor=element_blank(),
        plot.title=element_text(size=22,face="bold", vjust=2),
        axis.title=element_text(size=12,face = "bold"),
        axis.text=element_text(size=14))
       # scale_color_manual(values = c("AD" = "black", "YA" = "red")))
        #legend.position="none")
p3c
```

```{r}
ezANOVA(data=ADdata.means.liquid, dv=meanRR, wid=subID, within=c(liqType), between=age)
```

## Generalized Linear Mixed Effects Models: Reward Rate Effects by Liquid Incentive and Age
```{r}
# m.RR.liqxage<-glmer(formula = subRewarded ~ liqCode * age + (1+liqCode|subID),
#           data = ADdata, family = binomial)
# summary(m.RR.liqxage)
```


#13-15, 16-18, and young adult integration
```{r}
ADdata.means$agesplit = "adolescent"
YAdata.means$agesplit = "young adult"

ALLdata.means <- rbind(ADdata.means, YAdata.means)

RR.sumIntegration<-summarySEwithin2(data = ALLdata.means, measurevar = "meanRR", betweenvars = c("age", "agesplit"),
                        withinvars = c("money","liqType"), idvar = "subID")
RR.sumIntegration$age.group <- rep(c("13-15", "16-18", "young adult", "young adult"), each=27)

#RR.sumIntegration$agesplit<-factor(RR.sum$age, levels = c("adolescent","young adult"))

RR.sumIntegration2 <- summarySEwithin2(data= RR.sumIntegration, measurevar = "meanRR", betweenvars = c("age.group"), withinvars = c("money", "liqType"), idvar=c("age"))

figure3d <- ggplot(data = RR.sumIntegration2, aes(x = liqType, y = meanRR, fill = money)) +
  geom_bar(stat="identity", position = position_dodge(width = 0.8), width = 0.8, color = "black") +
  geom_errorbar(position=position_dodge(width=0.8), aes(ymin=meanRR-se, ymax=meanRR+se), width=.2) +  
  labs(x="Liquid",y="Reward Rate") +
      facet_grid(.~age.group, scales = "free_x") +
  #ggtitle("Task Performance Across Money") + 
  #scale_x_discrete(labels=c("younger","older")) +
  #scale_x_continuous(breaks=c(12:19), labels=c(13:18),limits=c(13,18)) + 
  coord_cartesian(ylim=c(.4,0.9)) +
  theme(panel.grid.minor=element_blank(),
        plot.title=element_text(size=22,face="bold", vjust=2),
        axis.title=element_text(size=14,face = "bold"),
        axis.text=element_text(size=8))
        #legend.position="none")

figure3d
```



# PLOT IV. (TB): INDIVIDUAL DIFFERENCES

#Adolescent reward rate by BIS
```{r}
#take an average reward rate per subject, plot with BIS/BAS
#use IndDiff

p4a<-ggplot(IndDiff, aes(x=BIS, y=meanRR)) + 
  geom_point(position=position_dodge(width=0.8)) +
  geom_smooth(method=lm, color = "red") +
  #geom_errorbar(position=position_dodge(width=0.8), aes(ymin=meanRR-se, ymax=meanRR+se), width=.2) +  
  labs(x="BIS Score",y="Average Reward Rate") +
    #ggtitle("Use theme(plot.title=element_text(hjust=0.5) to center") + theme(plot.title=element_text(hjust=0.5)) +
  #ggtitle("$ Reward Rate vs. BIS Score") + 
  #scale_x_discrete(labels=c("win","avoid losing")) +
  coord_cartesian(xlim=c(10,30)) +
  coord_cartesian(ylim=c(0,1)) +
  theme(#panel.background = element_blank(), panel.grid.major= element_blank(),
        panel.grid.minor=element_blank(),
        plot.title=element_text(size=18,face="bold", vjust=2),
        axis.title=element_text(size=12,face = "bold"),
        axis.text=element_text(size=10))
        #legend.position="none")

p4a
```

```{r}
z <- na.omit(IndDiff)
x<-z$BIS
y<-z$meanRR

cor.test(x,y)
```


```{r}
#BIS scores in $ conditions
subIDbis <- data.frame(IndDiff$subID, IndDiff$BIS)
oneDSbis <- subset(ADdata.means.money, ADdata.means.money$money == "$")
oneDSbis <- oneDSbis[-c(2),]
oneDSbis$BIS <- subIDbis$IndDiff.BIS

pOneDSbis<-ggplot(oneDSbis, aes(x=BIS, y=meanRR)) + 
  geom_point(position=position_dodge(width=0.8)) +
  geom_smooth(method=lm, color = "red") +
  #geom_errorbar(position=position_dodge(width=0.8), aes(ymin=meanRR-se, ymax=meanRR+se), width=.2) +  
  labs(x="BIS Score",y="$ Reward Rate") +
    #ggtitle("Use theme(plot.title=element_text(hjust=0.5) to center") + theme(plot.title=element_text(hjust=0.5)) +
  #ggtitle("$ Reward Rate vs. BIS Score") + 
  #scale_x_discrete(labels=c("win","avoid losing")) +
  coord_cartesian(xlim=c(10,30)) +
  coord_cartesian(ylim=c(0,1)) +
  theme(#panel.background = element_blank(), panel.grid.major= element_blank(),
        panel.grid.minor=element_blank(),
        plot.title=element_text(size=18,face="bold", vjust=2),
        axis.title=element_text(size=12,face = "bold"),
        axis.text=element_text(size=10))
        #legend.position="none")

#pOneDSbis

#BIS scores in $$ condition
twoDSbis <- subset(ADdata.means.money, ADdata.means.money$money == "$$")
twoDSbis <- twoDSbis[-c(2),]
twoDSbis$BIS <- subIDbis$IndDiff.BIS


pTwoDSbis<-ggplot(twoDSbis, aes(x=BIS, y=meanRR)) + 
  geom_point(position=position_dodge(width=0.8)) +
  geom_smooth(method=lm, color = "red") +
  #geom_errorbar(position=position_dodge(width=0.8), aes(ymin=meanRR-se, ymax=meanRR+se), width=.2) +  
  labs(x="BIS Score",y="$$ Reward Rate") +
    #ggtitle("Use theme(plot.title=element_text(hjust=0.5) to center") + theme(plot.title=element_text(hjust=0.5)) +
  #ggtitle("$$ Reward Rate vs. BIS Score") + 
  #scale_x_discrete(labels=c("win","avoid losing")) +
  coord_cartesian(xlim=c(10,30)) +
  coord_cartesian(ylim=c(0,1)) +
  theme(#panel.background = element_blank(), panel.grid.major= element_blank(),
        panel.grid.minor=element_blank(),
        plot.title=element_text(size=18,face="bold", vjust=2),
        axis.title=element_text(size=12,face = "bold"),
        axis.text=element_text(size=10))
        #legend.position="none")

#pTwoDSbis

#BIS scores in $$$$ condition
fourDSbis <- subset(ADdata.means.money, ADdata.means.money$money == "$$$$")
fourDSbis <- fourDSbis[-c(2),]
fourDSbis$BIS <- subIDbis$IndDiff.BIS


pFourDSbis<-ggplot(fourDSbis, aes(x=BIS, y=meanRR)) + 
  geom_point(position=position_dodge(width=0.8)) +
  geom_smooth(method=lm, color = "red") +
  #geom_errorbar(position=position_dodge(width=0.8), aes(ymin=meanRR-se, ymax=meanRR+se), width=.2) +  
  labs(x="BIS Score",y="$$$$ Reward Rate") +
    #ggtitle("Use theme(plot.title=element_text(hjust=0.5) to center") + theme(plot.title=element_text(hjust=0.5)) +
  #ggtitle("$$$$ Reward Rate vs. BIS Score") + 
  #scale_x_discrete(labels=c("win","avoid losing")) +
  coord_cartesian(xlim=c(10,30)) +
  coord_cartesian(ylim=c(0,1)) +
  theme(#panel.background = element_blank(), panel.grid.major= element_blank(),
        panel.grid.minor=element_blank(),
        plot.title=element_text(size=18,face="bold", vjust=2),
        axis.title=element_text(size=12,face = "bold"),
        axis.text=element_text(size=10))
        #legend.position="none")

#pFourDSbis

grid.arrange(pOneDSbis,pTwoDSbis,pFourDSbis, ncol=3, nrow=1, top = "BIS scores in $, $$, and $$$$ reward conditions")
```

#BIS vs. saltwater liking
```{r}
IndDiff <- cbind(ADsubjectMeans, SubjData)
juiceDiff <- cbind(ADjuiceMeans, SubjData)
saltwaterDiff <- cbind(ADsaltwaterMeans, SubjData)
neutralDiff <- cbind(ADneutralMeans, SubjData)

#IndDiff <- na.omit(IndDiff)
colnames(IndDiff)[colnames(IndDiff)=="Juice Likert"] <- "Juice.Likert"
colnames(IndDiff)[colnames(IndDiff)=="Saltwater Likert"] <- "Saltwater.Likert"
colnames(IndDiff)[colnames(IndDiff)=="Neutral Likert"] <- "Neutral.Likert"

BISsaltLike <- select(IndDiff, BIS, Saltwater.Likert)
BISsaltLike <- na.omit(BISsaltLike)
newID <- c(1:49)
BISsaltLike <- cbind(BISsaltLike, newID)

BISvSaltLiking<-summarySEwithin2(data = BISsaltLike, measurevar = "Saltwater.Likert", withinvars="BIS", idvar="newID")

p4c<-ggplot(BISvSaltLiking, aes(x=BIS, y=Saltwater.Likert)) + 
  geom_bar(position=position_dodge(width=0.8), color="black", stat="identity", width=0.8) +
  #geom_errorbar(position=position_dodge(width=0.8), aes(ymin=meanRR-se, ymax=meanRR+se), width=.2) +  
  labs(x="BIS score",y="Saltwater Likert Rating") +
  ggtitle("Saltwater Likert Rating vs. BIS score") + 
  #scale_x_discrete(labels=c("win","avoid losing")) +
  coord_cartesian(ylim=c(0.5,4.5)) +
  theme(panel.background = element_blank(), panel.grid.major= element_blank(),
        panel.grid.minor=element_blank(),
        plot.title=element_text(size=18,face="bold", vjust=2),
        axis.title=element_text(size=12,face = "bold"),
        axis.text=element_text(size=14))
       #legend.position="none")
p4c
```

